A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-31 2_related_work.tex
move thin geometric features paragraph up in related work
now the section ends in what our paper fixes

@@

% the context where our method can be positioned, and some related problems in that context
Under- and over-filling are especially problematic for thin geometric features.
\citeauthor{Jin2017a} proposed the use of a wavy path pattern for thin-walled parts~\cite{Jin2017a}.
This pattern is intended to be sparse. 
Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.

>>>>

% the context where our method can be positioned, and some related problems in that context
Under- and over-filling issues have a large proportional impact for thin geometric features.
\citeauthor{Jin2017a} proposed the use of a sparse wavy path pattern for thin-walled parts~\cite{Jin2017a}.
Besides under- and over-filling, there are a few other robustness issues in toolpath generation for thin geometric features.
\citeauthor{Moesen2011} proposed a method to make beam compensation more reliable for thin geometric features~\cite{Moesen2011}.
\citeauthor{Behandish2019a} presented a method to characterize local- topological discrepancies due to material under- and over-deposition, and used this information to modify the as-manufactured outcomes~\cite{Behandish2019a}.

@@
